Predicting Federal Emergency Management Agency Funding for U.S. Disasters

### 2021-11-29 products/manuscript/Manuscript_Disasters.Rmd
Manuscript Fix

## Model Performance Evaluation
The standard metric for evaluating regression models is the root mean square error (RMSE), which is the square root of the mean of the square of all error. It is formally defined as:
$$
RMSE = \sqrt{\frac {1}{n} \sum_{i = 1}^{n}{(S_i - O_i)^2}}
$$
where O_i are the observations, S_i are the predicted values of the outcome, and n is the number of observations in the analysis. RMSE is scale dependent, but the lower the RMSE, the better the model performance.

@@

The RMSEs for the testing and training datasets were substantially different, with an RMSE of 45003235 for the training data and 69378994 for the testing data. Figure \@ref(fig:BT-pred-act-test) shows the predicted and actual requested funds values, and Figure \@ref(fig:BT-pred-act-test-obl) does the same for obligated FEMA funds. The supplementary information contains the code for the models as well as all diagnostic plots.
```{r BT_pred_act_test,  fig.cap='Predicted vs actual requested FEMA funds for the bagged tree fit', echo=FALSE}
knitr::include_graphics("../../results/BT-pred-act-test.png")
```

>>>>

## Model Performance Evaluation
The standard metric for evaluating regression models is the root mean square error (RMSE), which is the square root of the mean of the square of all error. It is formally defined as:
$$
RMSE = \sqrt{\frac {1}{n} \sum_{i = 1}^{n}{(S_i - O_i)^2}}
$$
where O<sub>i</sub> are the observations, S<sub>i</sub> are the predicted values of the outcome, and n is the number of observations in the analysis. RMSE is scale dependent, but the lower the RMSE, the better the model performance.

@@

The RMSEs for the testing and training datasets were substantially different, with an RMSE of 45003235 for the training data and 69378994 for the testing data. Figure \@ref(fig:BT_pred_act_test) shows the predicted and actual requested funds values, and Figure \@ref(fig:BT_pred_act_test-obl) does the same for obligated FEMA funds. The supplementary information contains the code for the models as well as all diagnostic plots.
```{r BT_pred_act_test,  fig.cap='Predicted vs actual requested FEMA funds for the bagged tree fit', echo=FALSE}
knitr::include_graphics("../../results/BT-pred-act-test.png")
```
